---
title: "MLMResearch: Systematic Evaluation of Multilevel Meta-Analysis"
author: "Mahmood Ahmad"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MLMResearch Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
# library(MLMResearch)
```

## Introduction

The `MLMResearch` package provides a systematic framework for evaluating multilevel meta-analysis (MLMA) methods across empirical datasets. This vignette demonstrates the core workflow: testing methods, detecting issues, and applying adaptive solutions.

## 1. Using Pre-computed Evaluation Results

While `MLMResearch` can run tests across large cohorts, it also provides pre-computed evaluation results for demonstration and teaching purposes.

```{r}
# Load pre-computed evaluation results (mimicking output of run_dichotomous_tests)
data(mlm_eval_results)
head(mlm_eval_results)
```

## 2. Automated Issue Detection

The pre-computed results include flags for common methodological issues like variance collapse and convergence failures.

```{r}
# Summary of common issues detected in the evaluation
table(mlm_eval_results$variance_collapse)
table(mlm_eval_results$reml_converged)

# Example: Frequency of Variance Collapse (e.g., tau2 or omega2 = 0)
collapse_rate <- mean(mlm_eval_results$variance_collapse)
cat("Variance Collapse Rate: ", collapse_rate * 100, "%\n")
```

## 3. Applying Adaptive Methods

When standard methods fail (e.g., standard RVE in small samples), `MLMResearch` provides adaptive algorithms that automatically select the most robust estimation strategy based on the data's topology.

```{r, eval=FALSE}
# Extract a specific, problematic analysis
df_problem <- coh[coh$analysis_id == "Analysis_005", ]

# Standard RVE might have critically low degrees of freedom here
# The adaptive_rve function analyzes the cluster count and applies 
# the appropriate small-sample correction (e.g., CR2 with Satterthwaite df)
adaptive_result <- adaptive_rve(df_problem)

print(adaptive_result)
```

## Conclusion

By automating the evaluation of MLMA methods across hundreds of datasets, `MLMResearch` allows methodologists to empirically validate statistical theory and provides applied researchers with adaptive, "fail-safe" functions for complex evidence synthesis.
